humanCdGF_predict_cfu

### 2016-10-25 code/HumanCdGF_predict_cfu.Rmd
remove misc code

test <- data.frame(model = c('boruta',rep('reiterative_rf', 6),rep('one_mouse_per_cg',4)),
                   numOtus = c(length(boruta_otus), length(otus_used[[1]]),length(otus_used[[2]]),length(otus_used[[3]]),
                               length(otus_used[[4]]),length(otus_used[[5]]),length(otus_used[[6]]),30,27,6,2),
                   Rsq = c(tail(rf_boruta$rsq, 1), rf_rsq, 0.72, 0.71, 0.75, 0.71)
)
##### feature reduction #####
### boruta
set.seed(seed)
rf_features <- Boruta(log_cfu_med ~ ., data = cfu_shared_colonized.df, maxRuns = 2000)
boruta_otus <- names(rf_features$finalDecision)[rf_features$finalDecision == 'Confirmed']
set.seed(seed)
rf_boruta <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', boruta_otus)],
                           importance = TRUE, ntree = n_trees)
### above mean features, reiteratively reduce to 2 otus 
###### used mean because median results in including many low values in early OTU selection steps
rf_rsq <- c()
otus_used <- c()
rf_otus <- colnames(cfu_shared_colonized.df)[-1]
for(i in 1:100){
  if(length(rf_otus) > 1){
  set.seed(seed)
  rf <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', rf_otus)],
                     importance = TRUE, ntree = n_trees)
  rf_import_otus <- importance(rf, type = 1)
  otus_used[[i]] <- rf_otus
  rf_otus <- rownames(data.frame(rf_import_otus[rf_import_otus >= mean(rf_import_otus)]))
  rf_rsq[i] <- tail(rf$rsq, 1)
  } else {
    set.seed(seed)
    rf <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', rf_otus)],
                       importance = TRUE, ntree = n_trees)
    otus_used[[i]] <- rf_otus
    rf_rsq[i] <- tail(rf$rsq, 1)
    stop('Only one OTU remains')
  }
}
#### select top otus from reiteration through RF
optimum_otus <- otus_used[[which(rf_rsq == max(rf_rsq))]]
set.seed(seed)
rf_all <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', optimum_otus)],
                           importance = TRUE, ntree = n_trees)

reduced_otus <- otus_used[[3]]
set.seed(seed)
rf_all <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', reduced_otus)],
                           importance = TRUE, ntree = n_trees)

>>>>

##### feature reduction #####
### boruta
set.seed(seed)
rf_features <- Boruta(log_cfu_med ~ ., data = cfu_shared_colonized.df, maxRuns = 2000)
boruta_otus <- names(rf_features$finalDecision)[rf_features$finalDecision == 'Confirmed']
set.seed(seed)
rf_boruta <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', boruta_otus)],
                           importance = TRUE, ntree = n_trees)
### above mean features, reiteratively reduce to 2 otus 
###### used mean because median results in including many low values in early OTU selection steps
rf_rsq <- c()
otus_used <- c()
rf_otus <- colnames(cfu_shared_colonized.df)[-1]
for(i in 1:100){
  if(length(rf_otus) > 1){
  set.seed(seed)
  rf <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', rf_otus)],
                     importance = TRUE, ntree = n_trees)
  rf_import_otus <- importance(rf, type = 1)
  otus_used[[i]] <- rf_otus
  rf_otus <- rownames(rf_import_otus)[rf_import_otus >= mean(rf_import_otus)]
  rf_rsq[i] <- tail(rf$rsq, 1)
  } else {
    set.seed(seed)
    rf <- randomForest(log_cfu_med ~ ., data = cfu_shared_colonized.df[, c('log_cfu_med', rf_otus)],
                       importance = TRUE, ntree = n_trees)
    otus_used[[i]] <- rf_otus
    rf_rsq[i] <- tail(rf$rsq, 1)
    stop('Only one OTU remains')
  }
}
#### select top otus from reiteration through RF
optimum_otus <- otus_used[[which(rf_rsq == max(rf_rsq))]]
reduced_otus <- otus_used[[3]]
